### 2018-01-31 CO749-GraphColoring/assignments/A2.tex
finishing proof of 3, except one outstanding claim

\end{document}

>>>>

For every edge $e=uv \in E(G)$, $L(u) = L(v)$.
	TODO
We are now ready to complete the main proof. The argument is essentially the same as $2$-choosability of even cycles. From Claim $3.5$, let $L$ denote the constant list assigned to each vertex, i.e. $L = L(u)$ for each $u \in V(G)$. We know $|L|$ is even and we need to assign half its elements to each vertex.
 Let $S_1 \subseteq L$ be a subset of size $|L|/2$. Let $S_2 = L \backslash S_1$. Then $|S_1| = |S_2| = m(v)$ for any $v \in V(G)$. Enumerate the vertices about $G$ as $v_1, \dots, v_k$ with $k$ even. For each $v_i \in V(G)$, let $S(v) = S_1$ is $i$ is odd and $S(v) = S_2$ is $i$ is even. Since $G$ is an even cycle for any edge $v_iv_j \in E(G)$ exactly one of $i,j$ is odd and the other is even. Hence $S(v_i) \cap S(v_j) = \emptyset$, contradicting that $G$ is a counterexample.$\blacksquare$

\newpage
\section{}
\end{document}
